Graph Generators: State of the Art and Open Challenges

### 2020-01-23 main.tex
Updated affiliation Arnau Prat
New CSUR style

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

@@

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2019}
\acmMonth{0}

@@

% DOI
\doi{0000001.0000001}

%ISSN
\issn{0360-0300}

@@

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators: State of the Art and Open Challenges}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
%\title{Modern Graph Generators: A Survey}
\title{Graph Generators: State of the Art and Open Challenges}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{Sparsity-Technologies, Barcelona, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
Graph Generators: State of the Art and Open Challenges.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\begin{bottomstuff}
%This work is supported by ...
Author's addresses:
A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain;
S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
\end{bottomstuff}

@@

\tbl{Key characteristics of the generators} {

@@

\end{tabular} }

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               %& \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection\ }}
               %& \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & &  &  \\
\cline{2-7}
   & R-MAT    & {\bf x} & & &  &  \\
\cline{2-7}
   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
\cline{2-7}
  & GraphGen  & {\bf x} & & x &  & \\
\cline{2-7}
%  & Graph 500 & {\bf x} & & &  & \\
%\cline{2-7}
  & BTER      & {\bf x} & & &  & \\
\cline{2-7}
  & Darwini   & {\bf x} & & &  & \\
\cline{2-7}
  & RTG   & {\bf x} & & &  & x \\
\hline
\hline %  ======================  Semantic web
\multirow{16}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & LBBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & UOBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & IIMB & & {\bf x} & &  & \\
\cline{2-7}
 & BSBM & & {\bf x} & &  &  \\
\cline{2-7}
 & SP$^2$Bench & & {\bf x} & &  &  \\
\cline{2-7}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
\cline{2-7}
 & DBPSB & & {\bf x} & &  &  \\
\cline{2-7}
 & LODIB & & {\bf x} & &  &  \\
\cline{2-7}
% & SIB & & {\bf x} & &  &  \\
%\cline{2-7}
 & Geographica & & {\bf x} & &  &  \\
\cline{2-7}
 & WatDiv & & {\bf x} & &  &  \\
\cline{2-7}
 & RBench & & {\bf x} & &  &  \\
\cline{2-7}
  & S2Gen & & {\bf x} & &  &  \\
\cline{2-7}
  & RSPLab & & {\bf x} & &  &  \\
\cline{2-7}
 & LDBC SPB & & {\bf x} & &  &  \\
\cline{2-7}
 & LinkGen & & {\bf x} & &  &  \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x  &  \\
\cline{2-7}
  & gMark & & x & {\bf x} & x  &  \\
\cline{2-7}
  & graphGen & & & {\bf x} &  &  \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
\cline{2-7}
 & \cite{Yao2011}  & & & & {\bf x}  & \\
\cline{2-7}
 & LinkBench  & & & x & {\bf x}  & \\
\cline{2-7}
 & S3G2  & & x & x & {\bf x}  & \\
\cline{2-7}
 & SIB & & x & & {\bf x}  &  \\
\cline{2-7}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
\cline{2-7}
 & LDBC SNB   & & x & x & {\bf x}  & \\
\cline{2-7}
  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
%\hline
%\hline   % ======================   graph analytics
%\multirow{1}{*}{\rot{\textbf{A}}}
%  & HPC Scal. Graph Anal.  & & & & &  \\
%\cline{2-7}
%  & Graphalytics & & & & &  \\
\hline
\hline   %  ======================  community detection
\multirow{4}{*}{\rot{\textbf{Co}}}
  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
\cline{2-7}
  & LFR & x & & & &  {\bf x}  \\
\cline{2-7}
  & LFR-Overlapping & x & & & &  {\bf x} \\
\cline{2-7}
  & Stochastic Block Models & x & & & &  {\bf x} \\
%\cline{2-7}
%  & & & & &  \\
\hline
%\hline   %  ======================  streaming
%\multirow{2}{*}{\rot{\textbf{St}}}
%  & S2Gen & & & & & & & {\bf x}\\
%\cline{2-7}
%  & RSPLab & & & & & & & {\bf x} \\
%%\cline{2-7}
%%  & & & & & & \\
%\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{biblio}

@@

\end{document}

>>>>

%\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
\RequirePackage{rotating}
\documentclass[acmsmall]{acmart}

@@

% Metadata Information
%\acmVolume{0}
%\acmNumber{0}
%\acmArticle{0}
%\acmYear{2019}
%\acmMonth{0}

@@

% DOI
%\doi{0000001.0000001}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\setcopyright{acmcopyright}
\acmJournal{CSUR}
\acmYear{2020} \acmVolume{1} \acmNumber{1} \acmArticle{1} \acmMonth{1} \acmPrice{15.00}\acmDOI{10.1145/3379445}

%ISSN
%\issn{0360-0300}

@@

% Page heads
%\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators: State of the Art and Open Challenges}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
%\title{Modern Graph Generators: A Survey}
\title{Graph Generators: State of the Art and Open Challenges}

\author{Angela Bonifati}
\affiliation{%
  \institution{Lyon 1 University}
  \streetaddress{Liris CNRS Campus La Doua 23-25 Avenue Pierre de Coubertin}
  \city{Villerubanne}
  \postcode{69622}
  \country{France}
   }
\email{angela.bonifati@univ-lyon1.fr}

\author{Irena Holubov\'a}
\affiliation{%
  \institution{Charles University}
  \streetaddress{Faculty of Mathematics and Physics, Department of Software Engineering, Malostransk\'{e} n\'{a}m. 25}
  \city{Prague}
  \postcode{118 00}
  \country{Czech Republic}
  }
\email{holubova@ksi.mff.cuni.cz}

\author{Arnau Prat-P\'erez}
\affiliation{%
  \institution{Sparsity-Technologies}
  \streetaddress{Compte Guell 13}
  \city{Barcelona}
  \country{Spain}}
\email{aprat@ac.upc.edu}

\author{Sherif Sakr}
\affiliation{%
  \institution{University of Tartu}
  \streetaddress{J Liivi 2}
  \city{Tartu}
  \postcode{50409}
  \country{Estonia}
  }
\email{sherif.sakr@ut.ee}

\renewcommand{\shortauthors}{Bonifati, Holubov\'a, Prat-P\'erez, and Sakr}

%\author{
%ANGELA BONIFATI
%\affil{Lyon 1 University, France}
%IRENA HOLUBOV\'{A}
%\affil{Charles University, Prague, Czech Republic}
%ARNAU PRAT-P\'{E}REZ
%\affil{Sparsity-Technologies, Barcelona, Spain}
%SHERIF SAKR
%\affil{University of Tartu, Estonia}
%}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

%\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
%Graph Generators: State of the Art and Open Challenges.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

%\begin{bottomstuff}
%%This work is supported by ...
%Author's addresses:
%A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
%Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
%I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
%A. Prat-P\'erez, Sparsity-Technologies, Compte Guell 13, Barcelona, Spain;
%S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
%\end{bottomstuff}

@@

\caption{Key characteristics of the generators} 

@@

\end{tabular} 

@@

\begin{table}
\scriptsize
\centering
\caption{Overlapping of classes of generators} 
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               %& \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection\ }}
               %& \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & &  &  \\
\cline{2-7}
   & R-MAT    & {\bf x} & & &  &  \\
\cline{2-7}
   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
\cline{2-7}
  & GraphGen  & {\bf x} & & x &  & \\
\cline{2-7}
%  & Graph 500 & {\bf x} & & &  & \\
%\cline{2-7}
  & BTER      & {\bf x} & & &  & \\
\cline{2-7}
  & Darwini   & {\bf x} & & &  & \\
\cline{2-7}
  & RTG   & {\bf x} & & &  & x \\
\hline
\hline %  ======================  Semantic web
\multirow{16}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & LBBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & UOBM  & & {\bf x} & &  &  \\
\cline{2-7}
 & IIMB & & {\bf x} & &  & \\
\cline{2-7}
 & BSBM & & {\bf x} & &  &  \\
\cline{2-7}
 & SP$^2$Bench & & {\bf x} & &  &  \\
\cline{2-7}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
\cline{2-7}
 & DBPSB & & {\bf x} & &  &  \\
\cline{2-7}
 & LODIB & & {\bf x} & &  &  \\
\cline{2-7}
% & SIB & & {\bf x} & &  &  \\
%\cline{2-7}
 & Geographica & & {\bf x} & &  &  \\
\cline{2-7}
 & WatDiv & & {\bf x} & &  &  \\
\cline{2-7}
 & RBench & & {\bf x} & &  &  \\
\cline{2-7}
  & S2Gen & & {\bf x} & &  &  \\
\cline{2-7}
  & RSPLab & & {\bf x} & &  &  \\
\cline{2-7}
 & LDBC SPB & & {\bf x} & &  &  \\
\cline{2-7}
 & LinkGen & & {\bf x} & &  &  \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x  &  \\
\cline{2-7}
  & gMark & & x & {\bf x} & x  &  \\
\cline{2-7}
  & graphGen & & & {\bf x} &  &  \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
\cline{2-7}
 & \cite{Yao2011}  & & & & {\bf x}  & \\
\cline{2-7}
 & LinkBench  & & & x & {\bf x}  & \\
\cline{2-7}
 & S3G2  & & x & x & {\bf x}  & \\
\cline{2-7}
 & SIB & & x & & {\bf x}  &  \\
\cline{2-7}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
\cline{2-7}
 & LDBC SNB   & & x & x & {\bf x}  & \\
\cline{2-7}
  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
%\hline
%\hline   % ======================   graph analytics
%\multirow{1}{*}{\rot{\textbf{A}}}
%  & HPC Scal. Graph Anal.  & & & & &  \\
%\cline{2-7}
%  & Graphalytics & & & & &  \\
\hline
\hline   %  ======================  community detection
\multirow{4}{*}{\rot{\textbf{Co}}}
  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
\cline{2-7}
  & LFR & x & & & &  {\bf x}  \\
\cline{2-7}
  & LFR-Overlapping & x & & & &  {\bf x} \\
\cline{2-7}
  & Stochastic Block Models & x & & & &  {\bf x} \\
%\cline{2-7}
%  & & & & &  \\
\hline
%\hline   %  ======================  streaming
%\multirow{2}{*}{\rot{\textbf{St}}}
%  & S2Gen & & & & & & & {\bf x}\\
%\cline{2-7}
%  & RSPLab & & & & & & & {\bf x} \\
%%\cline{2-7}
%%  & & & & & & \\
%\hline
\end{tabular} 
\label{tab:overlapping}
\end{table}

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

@@

\end{document}
\endinput
